European or American? A re-examination of the transatlantic influence over the IMF

### 2025-05-27 demo/demo.qmd
adjust demo width
Adjust demo width for new form
change hypotheses

    -   $H_0$: No difference in the influence of US and Europe over the IMF.

    -   $H_1$: Either the US or EU has more influence over the IMF.

@@

@@

```{r results}
load('save/regTable.RData')
resultsTable |> tinytable::theme_tt("resize", width = 0.95)
```

>>>>

    -   $H_1$: Either the US or Europe has more influence over the IMF.

@@

    -   $H_2$: The US/Europe exerts a statistically significant influence on IMF lending decisions, controlling for European/American influence.

@@

```{r results}
load('save/regTable.RData')
resultsTable |> tinytable::theme_tt("resize", width = 0.81)
```
